preprocess_sketches THU

### 2020-09-03 analysis/step1_get_drawings/THU_Drawings/preprocess_sketches.Rmd
code to get filtered, object drawings for features/classifications

---
title: "preprocess_sketches"
author: "Bria Long"
date: "9/2/2020"
output: html_document
---

@@

```{r}
drawing_path = here::here('data/THU/drawings/full_set/')
filtered_dataset_path =  here::here('data/THU/drawings/filtered_dataset')
dir.create(filtered_dataset_path)
```

@@

drawing_info = all_drawings %>%
    mutate(fileNameShort = str_split_fixed(fullPath,"/",2)[,2]) %>%
    mutate(condition = str_split_fixed(fileNameShort,"_",2)[,1]) %>%
    mutate(category = str_split_fixed(fileNameShort,"_",3)[,2]) %>%
    mutate(raw_db_id = str_split_fixed(fileNameShort,"_",4)[,4]) %>%
    mutate(raw_db_id = str_split_fixed(raw_db_id,"_20",2)[,1]) %>%
    mutate(ID_Database = str_replace_all(raw_db_id,' ','')) %>%
    mutate(ID_Database = str_replace_all(ID_Database,'-','_'))  %>%
    mutate(ID_Database = str_replace_all(ID_Database,'__','_')) %>%
    mutate(ID_Database = str_replace_all(ID_Database,'I','i'))  %>%
    mutate(ID_Database = str_to_upper(ID_Database))  %>%
    mutate(iPad_Used = str_split(ID_Database,"[_]")[[1]][1],Short_SubID = str_split(ID_Database,"[_]")[[1]][2]) %>%
   select(ID_Database, better_filename, fileNameShort, fullPath, category, condition)

@@

```{r}
drawings_to_include <- drawing_info %>%
  left_join(demo, by=c('ID_Database')) %>%
  filter(!is.na(Age)) %>%
  mutate(age_group = floor(Age)) %>%
  mutate(better_filename = paste0(condition, '_',category, '_sketch_age',age_group, '_', ID_Database,'.png'))

@@

# copy included drawings and rename
```{r}
file.copy(fs::path(drawing_path, drawings_to_include$fullPath), fs::path(filtered_dataset_path, drawings_to_include$better_filename))
```

>>>>

---
title: "preprocess_sketches THU"
author: "Bria Long"
date: "9/2/2020"
output: html_document
---

@@

```{r}
drawing_path = here::here('data/THU/drawings/full_set/')
# filtered_dataset_path =  here::here('data/THU/drawings/filtered_dataset')
# filtered_dataset_path =  here::here('data/THU/drawings/object_drawings')
compiled_dataset_path = here::here('data/compiled/drawings/object_drawings')
# dir.create(filtered_dataset_path)
dir.create(compiled_dataset_path)
```

@@

drawing_info = all_drawings %>%
    mutate(fileNameShort = str_split_fixed(fullPath,"/",2)[,2]) %>%
    mutate(condition = str_split_fixed(fileNameShort,"_",2)[,1]) %>%
    mutate(category = str_split_fixed(fileNameShort,"_",3)[,2]) %>%
    mutate(raw_db_id = str_split_fixed(fileNameShort,"_",4)[,4]) %>%
    mutate(raw_db_id = str_split_fixed(raw_db_id,"_20",2)[,1]) %>%
    mutate(ID_Database = str_replace_all(raw_db_id,' ','')) %>%
    mutate(ID_Database = str_replace_all(ID_Database,'-','_'))  %>%
    mutate(ID_Database = str_replace_all(ID_Database,'__','_')) %>%
    mutate(ID_Database = str_replace_all(ID_Database,'I','i'))  %>%
    mutate(ID_Database = str_to_upper(ID_Database))  %>%
    mutate(iPad_Used = str_split(ID_Database,"[_]")[[1]][1],Short_SubID = str_split(ID_Database,"[_]")[[1]][2]) %>%
   select(ID_Database, fileNameShort, fullPath, category, condition)

@@

```{r}
practice_categories = c('triangle','this shape','this square','rectangle')

drawings_to_include <- drawing_info %>%
  left_join(demo, by=c('ID_Database')) %>%
  filter(!is.na(Age)) %>%
  mutate(age_group = floor(Age)) %>%
  mutate(better_filename = paste0(condition, '_',category, '_sketch_age',age_group, '_', ID_Database,'.png'))  %>%
  filter(!category %in% practice_categories)

@@

# copy included drawings and rename
```{r}
# file.copy(fs::path(drawing_path, drawings_to_include$fullPath), fs::path(filtered_dataset_path, drawings_to_include$better_filename))

file.copy(fs::path(drawing_path, drawings_to_include$fullPath), fs::path(compiled_dataset_path, drawings_to_include$better_filename))
```
